Extracting Function Signatures from Program Traces

### 2020-05-14 paper/main.tex
minor

\begin{abstract}
  Retrofitting a type system onto an existing dynamic language which was not
  designed to be statically typed is challenging. This paper takes the first
  step in the direction of designing a type system for the R programming
  language. We argue that R is particularly challenging due to its unique
  combination of features and to the programming idioms that have developped
  over the last two decades. As our starting point, we infer type signatures
  for \NUMFUNCTION functions from \NUMPACKAGES packages amongst the most
  widely used open source R libraries. The signatures use a minimal type
  language consisting of basic types, vectors, classes and disjunctions. We
  purposefully leave out notions such as subtyping, higher-order types, and
  polymorphism. Our goal is to understand what benefits a simple lanugage
  can yield.  We also implement a contract system that can use the inferred
  types to validate their correctness. We use the reverse depedencies of the
  packages to evaluate the benefits of typing.
\end{abstract}
\maketitle

@@

\AT{Leaving this one for Aviral.}

@@

\AT{I think we should move this to the Methodology section, which we should maybe rename to implementation. Thoughts?}

>>>>

\begin{abstract}
  Retrofitting a type system onto an existing dynamic language which was not
  designed to be statically typed is challenging. This paper takes the first
  step in the direction of designing a type system for the R programming
  language. We argue that R is particularly challenging due to its unique
  combination of features and to the programming idioms that have developped
  over the last two decades. As our starting point, we infer type signatures
  for \NUMFUNCTIONS functions from \NUMPACKAGES packages amongst the most
  widely used open source R libraries. The signatures use a minimal type
  language consisting of basic types, vectors, classes and disjunctions. We
  purposefully leave out notions such as subtyping, higher-order types, and
  polymorphism. Our goal is to understand what benefits a simple lanugage
  can yield.  We also implement a contract system that can use the inferred
  types to validate their correctness. We use the reverse depedencies of the
  packages to evaluate the benefits of typing.
\end{abstract}
\maketitle

@@

@@
